\huge \systemEnding: Growing Libraries of Concepts with Wake-Sleep Program Induction

### 2018-07-23 misc2.tex
More changes to the poster

  \textbf{Left column:} 16 out of 92 example tasks to hit in an all-or-none
  fashion --- training set for the \system algorithm.
  \textbf{Right column:} Learning curve for a run with a timeout of search time
  per task of 5 minutes (blue, bottom) and of 120 minutes (red, top). On the
  bottom are dreams, from left to right: before any training (original DSL, flat
  priors), at the end of the 5-minutes-timeout run, and at the end of the
  12-minutes-timeout run.

\end{column}
\begin{column}{\onecolwid} % The first column within column 2 (column 2.1)
  The agent controls a `pen' on a 2D plant. Primitives are those of the LOGO
  language, modified to have a functional programing structure.
\end{column}
\end{columns}

>>>>

  \textbf{Left column:} 16 out of 92 example tasks to hit in an all-or-none
  fashion --- training set for the \system algorithm.
  \textbf{Right column:} Learning curve for a run with a timeout of search time
  per task of 5 minutes (blue, bottom) and of 120 minutes (red, top). On the
  bottom are dreams, from left to right: before any training (original DSL, flat
  priors), at the end of the 5-minutes-timeout run, and at the end of the
  12-minutes-timeout run. \textbf{The color gradient} indicates the temporal
  aspect of the drawing part, or the pen, from blue (origin) to purple (end).

\end{column}
\begin{column}{\onecolwid} % The first column within column 2 (column 2.1)
  The agent controls a `pen' on a 2 dimentional plane. Primitives are those of
the LOGO language, modified to have a functional programing structure. Task
  don't take arguments (they are of type \texttt{unit -> image}) and the
  likelyhood function is all-or-none.

  Invented abstractions include:
  \begin{itemize}
    \item $\frac\pi2$ since it has $\pi$, $2$ and $/$ and needs right angles
    \item A line of any length followed with a right angle
    \item Loops of length $n$ that uses the number $n$ inside.
    \item A single line of unit length, followed by a set at the origin of the
      line
  \end{itemize}

  The deepest observed level of embedding of invented primitives on the 2 hours
  run was $7$, meaning that some invented primitives used invented and so on,
  seven times.
